---
title: "Linear model"
author: "Isai  Bercian"
date: "3/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)

```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 


```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

### Plot scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

## Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```
## Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```

The plot for ARM shows a reasonable fit points tend tobe scattered about the line.

```{r}
model1=lm(SIMS~ARM,data=data)
summary(model1)
```
Adjusted R-squared is 0.467.

```{r}
newdata=data.frame(GRIP=94, ARM=88)
predict(model1, newdata, interval="prediction")
```


### Plot scatterplot

```{r}
plot(SIMS~GRIP,data=data)
```

## Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```
## Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
```
The linear fit is not bad points tend to be scattered about the line.

```{r}
model2=lm(SIMS~GRIP,data=data)
summary(model2)
```

The adjusted R squared for GRIP only is 0.4053. This is smaller then the adjusted ARM R squared.

```{r}
predict(model2, newdata, interval="prediction")
```


The adjusted R square for model2 .4053, because this is smaller compared to model1 it just goes to show that model1 is a better fit.

# Inferential  (Build linear model)
  
```{r}
model3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model3)
```

The adjusted R squared is .5358. This is the largest out of all three models.

```{r}
anova(model1,model3)
```
The anova compares the two models the null hypothesis is no difference between the models the p-value is so small that we reject the null hypothesis. Based on residual standerd errors the model for ARM plus GRIP is better.
